Visualizing the Geography of Genetic Variants

### 2016-08-08 paper.tex
adjusting affiliation

\linenumbers
\captionsetup{labelfont=bf}
\frenchspacing
\title{Visualizing the Geography of Genetic Variants}
\author[1]{Joseph H. Marcus$^{*}$}
\author[1]{John Novembre\thanks{Address correspondence to JHM (\texttt{jhmarcus@uchicago.edu}) or JN (\texttt{jnovembre@uchicago.edu}).}}
\affil[1]{\small{Department of Human Genetics, University of Chicago, Chicago, IL,USA}}

>>>>

\linenumbers
\captionsetup{labelfont=bf}
\frenchspacing
\title{Visualizing the Geography of Genetic Variants}
\author[1]{Joseph H. Marcus$^{*}$}
\author[1,2]{John Novembre\thanks{Address correspondence to JHM (\texttt{jhmarcus@uchicago.edu}) or JN (\texttt{jnovembre@uchicago.edu}).}}
\affil[1]{\small{Department of Human Genetics, University of Chicago, Chicago, IL,USA}}
\affil[2]{\small{Department of Ecology and Evolutionary Biology, University of Chicago, Chicago, IL,USA}}
